Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-02-25 article-models-tt.tex
extended intro to tt

@@

\subsubsection{Extension on terms}
When $\jterm{\Gamma}{A}{x}$ and $\jterm{\Gamma}{\subst{x}{P}}{u}$ are terms,
we obtain a term $\jterm{\Gamma}{\ctxext{A}{P}}{\ctxext{x}{u}}$. This operation
of weakening on terms is like the pairing operation and like with the pairing
operation, extension on terms tells what the terms of an extended family are. 
However, it is handled
much stricter than $\smsym$-types, 
for it has a judgmental inverse and it is subject to various compatibility
rules.
\begin{align}
& \inference{\jterm{\Gamma}{A}{x}\quad\jterm{\Gamma}{\subst{x}{P}}{u}}{\jterm{\Gamma}{\ctxext{A}{P}}{\ctxext{x}{u}}}\\
& \inference{\jterm{\Gamma}{\ctxext{A}{P}}{w}}{\jterm{\Gamma}{A}{\pts{w}}}\\
& \inference{\jterm{\Gamma}{\ctxext{A}{P}}{w}}{\jterm{\Gamma}{\subst{\pts{w}}{P}}{\edg{w}}}\\
& \inference{\jterm{\Gamma}{\ctxext{A}{P}}{w}}{\jtermeq{\Gamma}{\ctxext{A}{P}}{\ctxext{\pts{w}}{\edg{w}}}{w}}\\
& \inference{\jterm{\Gamma}{A}{x}\quad\jterm{\Gamma}{\subst{x}{P}}{u}}{\jtermeq{\Gamma}{A}{\pts{(\ctxext{x}{u})}}{x}}\\
& \inference{\jterm{\Gamma}{A}{x}\quad\jterm{\Gamma}{\subst{x}{P}}{u}}{\jtermeq{\Gamma}{\subst{x}{P}}{\edg{(\ctxext{x}{u})}}{u}}
\end{align}

>>>>

In \autoref{extension-on-terms} we come back to the operation of extension, but
now for terms. The rules in this section explain what it means to be a term of
an extended family, namely to be an extended term. The compatibility rules for
extended terms are then similar as the compatibility rules that have appeared
earlier: there is a compatibility rule for the extension of an extension, for
the weakening of an extended term, for the substutution of an extended term by
an arbitrary term and for substitution by an extended term. The last set of
compatibility rules is a form of the Curry-Howard isomorphism -- this famous
correspondence naturally comes out of our scheme of compatibility rules.

@@

\subsubsection{Extension on terms}\label{extension-on-terms}
When $\jterm{\Gamma}{A}{x}$ and $\jterm{\Gamma}{\subst{x}{P}}{u}$ are terms,
we obtain a term $\jterm{\Gamma}{\ctxext{A}{P}}{\ctxext{x}{u}}$. This operation
of weakening on terms is like the pairing operation and like with the pairing
operation, extension on terms tells what the terms of an extended family are. 
However, it is handled
much stricter than $\smsym$-types, 
for it has a judgmental inverse and it is subject to various compatibility
rules.
\begin{align}
& \inference{\jterm{\Gamma}{A}{x}\quad\jterm{\Gamma}{\subst{x}{P}}{u}}{\jterm{\Gamma}{\ctxext{A}{P}}{\ctxext{x}{u}}}\\
& \inference{\jterm{\Gamma}{\ctxext{A}{P}}{w}}{\jterm{\Gamma}{A}{\pts{w}}}\\
& \inference{\jterm{\Gamma}{\ctxext{A}{P}}{w}}{\jterm{\Gamma}{\subst{\pts{w}}{P}}{\edg{w}}}\\
& \inference{\jterm{\Gamma}{\ctxext{A}{P}}{w}}{\jtermeq{\Gamma}{\ctxext{A}{P}}{\ctxext{\pts{w}}{\edg{w}}}{w}}\\
& \inference{\jterm{\Gamma}{A}{x}\quad\jterm{\Gamma}{\subst{x}{P}}{u}}{\jtermeq{\Gamma}{A}{\pts{(\ctxext{x}{u})}}{x}}\\
& \inference{\jterm{\Gamma}{A}{x}\quad\jterm{\Gamma}{\subst{x}{P}}{u}}{\jtermeq{\Gamma}{\subst{x}{P}}{\edg{(\ctxext{x}{u})}}{u}}
\end{align}
